---
title: "PlotlyProject"
author: "Endless-Void"
date: "7/31/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Some Plotly Graphs.

Hi. I just want to show you some graphs that i made using plotly and ggplot.

```{r libs, message=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2)
library(ggpubr)
library(plotly)
library(reshape2)
```


## Iris Data Set


According to the R documentation, the "iris" data set *"gives the measurements in centimeters of the variables sepal length and width and petal length and width, respectively, for 50 flowers from each of 3 species of iris. The species are Iris setosa, versicolor, and virginica."*

```{r striris}
str(iris)
```




## Scatter Plot.

```{r figure1, echo=FALSE}
fig1 <- ggplot(iris, aes(Sepal.Width, Sepal.Length)) +
        geom_point(aes(color = Species, fill = Species), pch = 21, size = 3.5,
                   alpha = 0.9) +
        scale_fill_manual("Species", 
                           values = c("setosa" = "white", 
                                      "versicolor" = "purple",
                                      "virginica" = "orange")) +
        scale_color_manual("Species", 
                          values = c("setosa" = "black", 
                                     "versicolor" = "black",
                                     "virginica" = "black")) + 
        ggtitle("Sepal Dimensions")
ggplotly(fig1)
```

## Density and Box Plots.

```{r figure2, message=FALSE, echo=FALSE}
den1 <- ggplot(iris, aes(x = Sepal.Length)) + 
        geom_density(aes(color = Species, fill = Species), alpha = 0.7) +
        scale_fill_manual("Species", 
                          values = c("setosa" = "white", 
                                     "versicolor" = "purple",
                                     "virginica" = "orange")) +
        scale_color_manual("Species", 
                           values = c("setosa" = "black", 
                                      "versicolor" = "black",
                                      "virginica" = "black")) +
        ggtitle("Sepal Length") + theme(legend.position = "none")

bp1 <- ggplot(iris, aes(x = Species, y = Sepal.Length)) + 
        geom_boxplot(aes(color = Species, fill = Species)) +
        scale_fill_manual("Species", 
                          values = c("setosa" = "white", 
                                     "versicolor" = "purple",
                                     "virginica" = "orange")) +
        scale_color_manual("Species", 
                           values = c("setosa" = "black", 
                                      "versicolor" = "black",
                                      "virginica" = "black")) +
        ggtitle("Sepal Length") + theme(legend.position = "none")

den2 <- ggplot(iris, aes(x = Sepal.Width)) + 
        geom_density(aes(color = Species, fill = Species), alpha = 0.7) +
        scale_fill_manual("Species", 
                          values = c("setosa" = "white", 
                                     "versicolor" = "purple",
                                     "virginica" = "orange")) +
        scale_color_manual("Species", 
                           values = c("setosa" = "black", 
                                      "versicolor" = "black",
                                      "virginica" = "black")) +
        ggtitle("Sepal Width") + theme(legend.position = "none")

bp2 <- ggplot(iris, aes(x = Species, y = Sepal.Width)) + 
        geom_boxplot(aes(color = Species, fill = Species)) +
        scale_fill_manual("Species", 
                          values = c("setosa" = "white", 
                                     "versicolor" = "purple",
                                     "virginica" = "orange")) +
        scale_color_manual("Species", 
                           values = c("setosa" = "black", 
                                      "versicolor" = "black",
                                      "virginica" = "black")) +
        ggtitle("Summary of Sepal Dimensions") + theme(legend.position = "none")

subplot(den1, bp1, den2, bp2, nrows = 2)
```

## EuStockMarkets Data Set.

According to the R documentation, the "EuStockMarkets" data set: *"Contains the daily closing prices of major European stock indices:* 

- *Germany DAX (Ibis)*

- *Switzerland SMI.*

- *France CAC.*

- *UK FTSE.*

*The data are sampled in business time, i.e., weekends and holidays are omitted."*

## Time Series Plots.

```{r figure3, echo=FALSE, message=FALSE, warning=FALSE}
ESM <- data.frame(Date = time(EuStockMarkets), 
                  as.matrix(EuStockMarkets))
ESM <- melt(data = ESM, id.vars = "Date", 
            measure.vars = c("DAX", "SMI", "CAC", "FTSE"))

fig3 <- ggplot(ESM, aes(x = Date, y = value)) + 
        geom_line(aes(color = variable)) +
        scale_color_manual("European stock indices", 
                          values = c("DAX" = "green", 
                                     "SMI" = "purple",
                                     "CAC" = "orange",
                                     "FTSE" = "black")) +
        ylab("Closing Price") + 
        ggtitle("Daily Closing Prices of European Stock Indices")
ggplotly(fig3)
```

## THE END.

Hope you liked.

Ty :3